Source Summaries

### 2020-02-10 paper/sourceSummaries/summary2.tex
added my summary for week2

\noindent
\subsection{{S}urvey on {V}arious {D}oor {L}ock {A}ccess {C}ontrol {M}echanisms}

@@

\noindent
Joshua Niemann

@@

\Urlmuskip=0mu plus 1mu\relax
\bibentry{matthewrs2017surveydoorlock}

@@

\noindent
The authors compare different types of door lock authentication measures and their overall security.

@@

\noindent
The authors are applying Game Theory by directly comparing each individual authentication method.

@@

\noindent
The authors directly compare different authentication methods using different factors.  These can include battery life, cryptographic and mechanical security, the concern of a passed credential, and what happens if an authentication token is lost.

@@

\noindent
The authors found that each system has individual strengths.  As each method does better in different ways, emphasis is placed on ensuring the use of the lock that is best suited for the use case in which it is placed.  Factors considered include but are not limited to whether a physical key is required, whether or not the key will be passed off to a third party user, and if the system would be considered secure for the given use case.

@@

\noindent
The authors suggest using the knowlege of authentication system problems in order to build a new system, taking in mind the strengths and weaknesses for each category of authentication.

>>>>

\subsection{Security Vulnerabilities of Bluetooth Low Energy Technology (BLE)}

@@

\noindent
Jacob Ruud

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{o'sullivan}

@@

\noindent
Author Harry O'Sullivan along with mentor Ming Chow attempt to analyze the security of bluetooth low energy technology. They focus specifically on how BLE devices communicate with each other and how the communication between devices could be exploited by attackers.

@@

\noindent
O'sullivan applies Game Theory in his work on BLE devices. Posing as an attacker he and attempts to simulate attack scenarios treating a compromise of sensitive information as a win.

@@

\noindent
The author presents three different methods to compromise BLE as part of his research. The first method he attemps is an eavesdropping attack, during which he tries to capture information about a bluetooth host device using a sniffer. The second attack method he outlines is Man-in-the-middle, to explain which he refers to research done by lecturers at Marthandam College. The third attack scenario he describes is denial of service. During his explaination he outlines work done by researchers at University of Utah, as well as an attack technique called fuzzing.

@@

\noindent
The main findings ot this paper present the vulnerabilities of the BD_ADDR field which is present in all BLE communication. O'Sullivan found that an attacker could use bluetooth fuzzing to determine the master source of a bluetooth connection and potentially forge a connection to it. Not to mention the fact that BD_ADDR's are not globally unique so an attacker could try to spoof their BD_ADDR until packets start flowing in.

@@

\noindent
The author does not include any future directions at the end of his work. Bluetooth Low Energy has been tested extensively since its inception, and I can only assume that O'Sullivan believes that there is work out there testing every corner or bluetooth low energy. I do not necessarily agree with his thoughts but that is all there is to report with this paper.
